### 2017-11-29 Docs/Thesis/docs/chapter3.tex
update

\begin{figure}
\centering
\subfloat[first]{
  \includegraphics[height=4.in]{figures/ch3/cdt1}
}
\subfloat[second]{
  \includegraphics[height=4.in]{figures/ch3/cdt2}
}
\caption{Directory diagram of the schema of a Compact Trace Descriptor (CDT) file. On the left, we present a dissected flow, and on the right a set of flows.}
\label{fig:CTD-diagram}
\end{figure}

@@

The Flow Generator handles the data on the \textit{Compact Trace Descriptor} file, and use to retrieve parameters for traffic generation. It crafts and controls each flow in a separated thread. To valitate its operation we implemented using Iperf traffic generation\cite{web-iperf} and Libtins C++ API.  To simplify the expansion of this component, we use the design pattern factory. If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}. The new class must not have any new attribute.  Support for this class must be given in the \texttt{NetworkFlowFactory} class.

This component works in two different layers according to the traffic generators classification introduced in the chapter ~\ref{ch:literature-review}: at the Flow level, and packet level, as presented in the figure ~\ref{fig:layers-workload-tools}.

@@

At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}. This algorithm handles our model defined at the figure~\ref{fig:modified-harpoon-model}. This procedure is independet of the traffic generator being used.

It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps for \texttt{start\_delay} seconds. This is the arrival time of the first flow packet. Passed this time, it then calls the underlying traffic generation tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface. Then it sleeps the next session OFF time. When the list of ON/OFF times from the flow is over, the thread ends.

At the packet level, the  \texttt{DummyFlow} derived class must implement  a new \texttt{flowGenerate()} method. Here, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}. This method must use the available parameters, atributes and \textit{getters} to configure and generate a thread-safe traffic.  The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic. We call this concept \textit{Flow Generation Programming} A more complex configuration is possible, but it serves to illustrate the procedure. Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}. 
\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{c++}

@@

	//configure inter-packet time model, just Weibull or Constant
	for(uint i = 0;;i++)
	{	
		StochasticModelFit idtModel = getInterDepertureTimeModel(i);
		if(idtModel.modelName() == WEIBULL)
		{
			strCommand += " -W " + std::to_string(idtModel.param1()) + " " + std::to_string(idtModel.param2());
			break;
		}
		else if ( idtModel.modelName() == CONSTANT)
		{
			strCommand += " -C " + std::to_string(nbytes/(1024*onTime));
			break;
		}
	}

	// it uses C strings as arguments
	// it is not blocking, so it must block until finishes
	int rc = DITGsend(localhost.c_str(), command.c_str()); 
    usleep(onTime*10e6); // D-ITG uses miliseconds as time unity
	if (rc != 0)
	{
		PLOG_ERROR << "DITGsend() return value was" << rc ; // our log macro for erros
		exit(EXIT_FAILURE);
	}
}
\end{minted}

@@

A network traffic generator software that should provide its API or script interface for the \textit{FlowGenerator} component.

Since \texttt{DITGsend()} is thread safe, no mutex is need. It would be needed if a lower level API, such Libtins or Libpcap was used. In that case, these APIs would permit control precisely each packet sent through the interface, but a mutex would be necessary. An scriptable tool, such as Iperf can be used as well, using \texttt{fork()} or \texttt{popen()}.

As we claimed before, this tools is simple of being expanded for almost any traffic generation API, since its modeling framework is not coupled to the traffic generation.
The figure \ref{fig:network-trace-flow-class-diagram} illustrates it well. It presents three possibilities of different traffic generation engines, all being configured and scheduled in a platform-agnostic way.

@@

When it working as a sniffer, it strores data from the capture traffic in the sqlite3 database. It may work over a \textit{pcap} file or an Ethernet interface. Working as a trace a trace-analyzer, it receive the name of the trace as stored in the database, and creates a XML compact trace descriptor. The constants used in the modelling may be changed and provided as command line argument. If not, the default values will be used.

As a traffic generator it may work as a client or a server. Working as a server is necessary for tools that require establishing a connection before generate the traffic, such as Iperf and D-ITG. It will just work passivaly. Working as a client, is acts as a traffic emissor. Tools such as \textit{libtins} dos not require server operation the send the traffic.

When it operates as a client or as packet injector, it is operating as a traffic generator. The difference is that as a client, the used traffic generator is connection-oriented. It needs to establish a connection with the destination host (the server), before start sending packets. Operating as a client, it must take as an input a list of IP or MAC destination addresses, since they will not match with the ones in the original trace. It takes as an input a single destination in the command line, or list of many, in a text file passes as a parameter. Also, it uses the machine IP address as packet's source IP.

 As a packet injector can generate packets on the output interface, without establishing a connection. It uses the original IP and MAC destination and source addresses. As a client, the reproduction of the trace is expected to be poor in the flow level metrics exposed in the chapter ~\ref{ch:literature-review}, since it will use new addresses values.

The operation of packet injector is still under implementation, and we are using Libtins API. Currently, SIMITAR supports client mode with D-ITG, implemented using its C++ API. We intend to provide support for many others traffic generators, such Iperf and Ostinato.

When operating as a server, it just start-up the traffic generator server, and waits forclient requests for connections. Down bellow, we present simple examples of commands used to activate each operation mode.

@@

As use cases, we can cite:

\begin{itemize}

\item Flow Generation Progamability: creation of custom synthetic traffic with a certain number of flows, in a traffic-generator independent way.

\item Generate Background traffic with D-ITG: SIMITAR can work to generate background traffic over a network when it receives many addresses as input. If each destination is reachable, D-ITG will establish a connection with each destination, and recreate flows as described in the CDT file.

\item Stress a Device Under Test (DUT): It can be used to stress a single device with a more self-similar realistic traffic. The CDT file can be manually modified to change some aspects of the traffic, such as the number os packets or throughput applied by the traffic generator of each flow. Some undesirable features such as Stochastic models or lesser flow may be taken out, SIMITAR does not have constraints on a number of flows and Stochastic models adopted (but must have at least one).

\item Generate synthetic \textit{pcap} files: Using virtual interfaces, we can reproduce a traffic, and capture it with a sniffer tool, such as Tcpdump, Wireshark or Tshark. We plan to automatize this process as a future work, with an operation mode of \textit{pcap} generator. To do this we are going to use Mininet to create the virtual interfaces and Libtins to inject packets.

\end{itemize}

>>>>

\begin{figure}
\centering
\subfloat[]{
  \includegraphics[height=4.in]{figures/ch3/cdt1}
}
\subfloat[]{
  \includegraphics[height=4.in]{figures/ch3/cdt2}
}
\caption{Directory diagram of the schema of a Compact Trace Descriptor (CDT) file. On the left, we present a dissected flow, and on the right a set of flows.}
\label{fig:CTD-diagram}
\end{figure}

@@

@@

The Flow Generator handles the data on the \textit{Compact Trace Descriptor} file, and use to retrieve parameters for traffic generation. It crafts and controls each flow in a separated thread. We already implemented this component using Iperf traffic generator and Libtins C++ API, and it must follow the calss hierarcy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.  This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ). On our current implementation we already have implemented \texttt{IperfFlow} and \texttt{TinsFlow}, and \texttt{DitgFlow} is under validation process. This new class has the requirement of not have any new attribute. The support for this new class must be given on the factory class \texttt{NetworkFlowFactory}. For closed loop packet-crafters (that means, tools which must establish a connection between the source and the destination), two methods must be implemented: \texttt{flowGenerate()} and \texttt{server()}. \texttt{flowGenerate()} is responsible for sending a \textit{file}, as defined on de figure~\ref{fig:modified-harpoon-model}, and \texttt{server()} to receive $n$ files. Open loop packet-crafters, such as we implemented using Libtins (just sent the packets, do not establishes a connection), the server do not need to be implemented.}.

This component and therefore our traffic generator is a multi-layer workload generator according to the typing introduced on chapter ~\ref{ch:literature-review} \footnote{Since it works both at packet and flow level, but do not work at application level.}. At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{fig:alg-simplified-harpoon}. This algorithm handles our model defined at the figure ~\ref{fig:modified-harpoon-model}. This procedure is independent of the underlying packet crafting tool used. It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps for \texttt{start\_delay} seconds. This is the arrival time of the first flow packet. Passed this time, it then calls the underlying traffic generation tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface. Then it sleeps the next session OFF time. When the list of ON/OFF times from the flow is over, the thread ends.

At the packet level, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}. This method must use the available parameters, attributes and \textit{getters} to configure and generate a thread-safe traffic using the method \texttt{flowGenerate()}. The \textit{file} configuration must follow the in the figure ~\ref{fig:alg-traffic-engine-config}.  Down below we present a simple code of how the D-ITG API can be used to generate packet-level traffic. A more complex configuration is possible, but it serves to illustrate the procedure. We call this concept \textit{Flow Generation Programming}.  Its API documentation is available at on D-ITG website \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}.

\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{c++}

@@

	//configure inter-packet time model, just Weibull or Constant
	StochasticModelFit idtModel;
	for(uint i = 0;;i++)
	{	
		idtModel = this->getInterDepertureTimeModel(i);
		if(idtModel.modelName() == WEIBULL)
		{
			strCommand += " -W " + std::to_string(idtModel.param1()) + " " + std::to_string(idtModel.param2());
			break;
		}
		else if ( idtModel.modelName() == CONSTANT)
		{
			strCommand += " -C " + std::to_string(nbytes/(1024*onTime));
			break;
		}
	}

	// it uses C strings as arguments
	// it is not blocking, so it must block until finishes
	int rc = DITGsend(localhost.c_str(), command.c_str()); // D-ITG API
    usleep(onTime*10e6); // D-ITG uses miliseconds as time unity
	if (rc != 0)
	{
		PLOG_ERROR << "DITGsend() return value was" << rc ; // our log macro for erros
		exit(EXIT_FAILURE);
	}
}
\end{minted}

@@

A network traffic generator software that should provide its API or script interface for the \textit{FlowGenerator} component. With this tool, the user must be eble to send packets/traffic and controll atributes, such as sending time, bandwidht, number of packets, protocols, and so on. That means, any available parameter form the compact trace descriptor. If it does not have an API but an CLI, the user may have to use functions such as \texttt{fork()} or \texttt{popen()}.

@@

When it working as a sniffer, it stores data from the captured traffic in the sqlite3 database. It may work over a \textit{pcap} file or an Ethernet interface. Working as a trace a trace-analyzer, it receives the name of the trace as stored in the database, and creates an XML compact trace descriptor. The constants used in the modeling may be changed and provided as command line argument. If not, the default values will be used. As a traffic generator, it may work as a client or a server. Working as a server is necessary for closed-loop engines; tools that require establishing a connection before generating the traffic, such as Iperf and D-ITG. It will just work passively. Working as a client is acting as a traffic emitter. Open loop packet-crafter tools such as \textit{libtins} does not require server operation the send the traffic. In the case of closed-loop tools, the destination IP addresses must be explicitly given in the command line by the options \texttt{--dst-list-ip} or \texttt{--dst-ip}. Down below, we present simple examples of commands used to activate each operation mode.

@@

### 2017-11-29 Docs/Thesis/docs/chapter6.tex
update

\begin{table}[ht!]
	\centering
	\caption{Future Work: task list}
	\label{tab:task-list}
	\begin{tabular}{cccc}
		\hline
		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
		1                      & Optimizing linear regression                              &                                                 & \textit{high}                    \\
		2                      & Flow-merging option                                       &                                                 & medium                  \\
		3                      & Smart flow-scheduler                                      &                                                 & \textit{high}                    \\
		4                      & \texttt{DataProcessor::minimumAmountOfPackets}                         &                                                 & low                     \\
		5                      & DPDK KNI interfaces                                       &                                                 & medium                     \\
		6                      & Multi-thread C++ sniffer                                  & \multirow{-6}{*}{Performance}                   & \textit{high}                    \\ \hline
		7                      & Model inter-packet times on \texttt{TinsFlow}           &                                                 & \textit{high}                    \\
		8                      & D-ITG flow generator (\texttt{DitgFlow})                &                                                 & low                     \\
		9                      & DPDK flow generator (\texttt{DpdkFlow})                 &                                                 & medium                     \\
		10                     & Ostinato flow generator (\texttt{OstinatoFlow})         & \multirow{-4}{*}{Tool support}                  & low                     \\ \hline
		11                     & \texttt{DataProcessor::min\_time}                       &                                                 & low                     \\
		12                     & \texttt{DataProcessor::m\_min\_on\_time}                &                                                 & low                     \\
		13                     & \texttt{DataProcessor::m\_session\_cut\_time}           &                                                 & low                     \\
		14                     & Minimum number of packets per flow option                 & \multirow{-4}{*}{Calibration}  & low                     \\ \hline
		15 & Python API/Lua for traffic generation & & low \\
		16 & Crafter of  pcap files & \multirow{-2}{*}{New features} & low \\
		%17 & Json compact trace descriptor  & \multirow{-3}{*}{New features} & low 
		\hline
	\end{tabular}
\end{table}

@@

(7) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times. To avoid overheads on random numbers calculation,  these values must be calculated before the actual traffic generation. Modelling inter-packet times the scaling characteristics of libtins traffic should improve.

(8-10) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}. D-ITG offers many stochastic functions for customization of inter-packet times, Ostinato provides a rich set of headers and protocols, and DPDK a high performance on packet generation. Each tool can offer a different result on traffic generation, each with benefits and drawbacks, such as computational cost, and development complexity.  Also, DPDK provides the possibility to bypass the Linux network stack, called packet acceleration. So, this implementation can enable for SIMITAR high-bandwidth along with traffic realism.

(11) Calibrate  the constant  \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times. We use this value to avoid inter-packet times equals to zero due to the sniffer resolution. A zero-inter-packet time would make the procedure fail.  This value can change the fitting accuracy. Today, this value is $5e-8$.

(12) Calibrate  the constant \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have. It can change the generated traffic precision. Currently this value is $0.1$s.

(13) Calibrate  the constant \texttt{DataProcessor::m\_session\_cut\_time}: this value defines whatever a file transference still active or has ended. It defines the smallest OFF time acceptable. This value will change how many files SIMITAR will transfer per flow, and how many times it will call the underlying traffic generator. This constant affects the computational performance and traffic realism.

(14) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance. Since SIMITAR manages each flow in a different thread, it will create fewer threads simultaneously, reducing overheads. This action should not impact on throughput and scaling characteristics because few packets would be ignored. But it can increase the precision of the most significant flows since all the threads are competing for each other on the Operational System. But, the number of flows created would be smaller.

(15) Currently, SIMITAR only enables the programming of flow traffic generation in C++. Adding Python and Lua support for the Flow Generator component, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.

(16) \textbf{PcapGen: a compact \textit{pcap} lybrary}: Create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors(CTDs) files. We can implement this using SIMITAR as a packet injector, but in an emulated host interface, for example, using Mininet. Then, the traffic can be collected, using a tool such as TCPDump or Tshark. We present a diagram of this idea in the figure ~\ref{fig:pcap-gen}. This expansion would enable SIMITAR  to work as trace library for pcap-based benchmark tools.

>>>>

\begin{table}[ht!]
	\centering
	\caption{Future Work: task list}
	\label{tab:task-list}
	\begin{tabular}{cccc}
		\hline
		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
		1   & Optimizing linear regression                      &                                & \textcolor{red}{high} \\
		2   & Flow-merging option                               &                                & medium \\
		3   & Smart flow-scheduler                              &                                & \textit{high} \\
		4   & \texttt{DataProcessor::minimumAmountOfPackets}    &                                & low \\
		5   & DPDK KNI interfaces                               &                                & medium \\
		6   & Multi-thread C++ sniffer                          &                                & \textit{high} \\ \hline
		7   & Cluster operation (high speed traffic-gen) & \multirow{-7}{*}{Performance}  & \textit{high} \\
		8   & Model inter-packet times on \texttt{TinsFlow}     &                                & \textit{high} \\
		9   & D-ITG flow generator (\texttt{DitgFlow})          &                                & low \\
		10  & DPDK flow generator (\texttt{DpdkFlow})           &                                & medium \\
		11  & Ostinato flow generator (\texttt{OstinatoFlow})   & \multirow{-4}{*}{Tool support} & low \\ \hline
		12  & \texttt{DataProcessor::min\_time}                 &                                & low \\
		13  & \texttt{DataProcessor::m\_min\_on\_time}          &                                & low \\
		14  & \texttt{DataProcessor::m\_session\_cut\_time}     &                                & low \\
		15  & Minimum number of packets per flow option         & \multirow{-4}{*}{Calibration}  & low \\ \hline
		16  & Python API/Lua for traffic generation             &                                & low \\
		17  & Crafter of  pcap files                            & \multirow{-2}{*}{New features} & low \\

		\hline
	\end{tabular}
\end{table}

@@

(7) Since the \textit{compact trace descriptor} describes $n$ different flows, it can be splitted on $m$ different files, each describing $n/m$ flows, and still describe the same traffic. With $m$ synchronized machines woking in parallel, each using one of these $m$ parts of the original \textit{compact trace descriptor}, with use of link-agregattion techinique\footnote{http://www.comutadores.com.br/configurando-link-aggregationetherchannel-entre-cisco-e-hpn/} we can achieve high speeds on bare-metal.

(8) SIMITAR's current implementation using \textit{libtins} to generate the packets does not model inter-packet times. To avoid overheads on random numbers calculation,  these values must be calculated before the actual traffic generation. Modelling inter-packet times the scaling characteristics of libtins traffic should improve.

(9-11) Expand SIMITAR to other traffic generator tools, as we present in the figure ~\ref{fig:DpdkFlow}. D-ITG offers many stochastic functions for customization of inter-packet times, Ostinato provides a rich set of headers and protocols, and DPDK a high performance on packet generation. Each tool can offer a different result on traffic generation, each with benefits and drawbacks, such as computational cost, and development complexity.  Also, DPDK provides the possibility to bypass the Linux network stack, called packet acceleration. So, this implementation can enable for SIMITAR high-bandwidth along with traffic realism.

(12) Calibrate  the constant  \texttt{DataProcessor::min\_time}: smallest time considered for inter-packet times. We use this value to avoid inter-packet times equals to zero due to the sniffer resolution. A zero-inter-packet time would make the procedure fail.  This value can change the fitting accuracy. Today, this value is $5e-8$.

(13) Calibrate  the constant \texttt{DataProcessor::m\_min\_on\_time}: this value controls the small ON time that a \textit{file} can have. It can change the generated traffic precision. Currently this value is $0.1$s.

(14) Calibrate  the constant \texttt{DataProcessor::m\_session\_cut\_time}: this value defines whatever a file transference still active or has ended. It defines the smallest OFF time acceptable. This value will change how many files SIMITAR will transfer per flow, and how many times it will call the underlying traffic generator. This constant affects the computational performance and traffic realism.

(15) Constant \textit{Control a minimum number of packets required for SIMITAR create a new flow}: this would reduce the number of flows created, improving its computational performance. Since SIMITAR manages each flow in a different thread, it will create fewer threads simultaneously, reducing overheads. This action should not impact on throughput and scaling characteristics because few packets would be ignored. But it can increase the precision of the most significant flows since all the threads are competing for each other on the Operational System. But, the number of flows created would be smaller.

(16) Currently, SIMITAR only enables the programming of flow traffic generation in C++. Adding Python and Lua support for the Flow Generator component, we can enable expansion for Python/Lua traffic generation APIs (such as Ostinato and MoonGen APIs), without creating C++ wrappers.

(17) \textbf{PcapGen: a compact \textit{pcap} lybrary}: Create a component capable of generate synthetic \textit{pcap} files, using Compact Trace Descriptors(CTDs) files. We can implement this using SIMITAR as a packet injector, but in an emulated host interface, for example, using Mininet. Then, the traffic can be collected, using a tool such as TCPDump or Tshark. We present a diagram of this idea in the figure ~\ref{fig:pcap-gen}. This expansion would enable SIMITAR  to work as trace library for pcap-based benchmark tools.
